Towards Enriching Robot's Actions with Affective Movements

### 2017-01-05 HRI-LBR/HRI-LBR2017.tex
addition and correction of some sentences

The system has been implemented in C++ and interfaced with ROS %TODO Cite, I would like to add them but the space is tight Andy- OK it is not needed
. To fulfill all the requirements, the system was implemented in two different nodes %TODO Here teh term node might be misleading. Maybe ROS node would be better
: one containing the enrichment system, and the second an interface to connect the system with diverse platforms. The system has been tested in two physical platforms, with different degrees of freedom: Triskarino%TODO Cite Andy-You may also just cite our paper already in the list. There are no papers specific to this platform.
 and Keepon\footnote{ The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}. The simple actions implemented in the system were: \textit{do nothing} waits for a time $t$ before it communicates a finish message; \textit{move body} moves the platform from its current position $a$ to a desired position $b$; \textit{oscillate body} generates an oscillation in the whole platform by an angle $\theta$; \textit{move shoulder} moves the shoulders to a desired angle $\theta$; \textit{oscillate shoulder} oscillates the shoulders by a given angle $\theta$; \textit{move torso} moves the torso to a desired angle in $yaw$, $pitch$ and $roll$; and \textit{oscillate torso} oscillates the shoulders by a given angle $\theta$. %TODO Andy-a sentence about how the drivers could apply the description to these two so different platforms (e.g., Keepon is not moving) would be needed.

>>>>

The system has been implemented in C++ and interfaced with ROS %TODO Cite, I would like to add them but the space is tight Andy- OK it is not needed
. To fulfill all the requirements, the system was implemented in two different ROS nodes %TODO Here teh term node might be misleading. Maybe ROS node would be better
: one containing the enrichment system, and the second an interface to connect the system with diverse platforms. The system has been tested in two physical platforms, with different degrees of freedom: Triskarino~\cite{angel2013}
 and Keepon\footnote{ The code is available in the repository \url{https://github.com/julianangel/EmotionBot/tree/master/ROS/theatrebot_action_modulation}}.

The simple actions implemented in the system were: \textit{do nothing} waits for a time $t$ before it communicates a finish message; \textit{move body} moves the platform from its current position $a$ to a desired position $b$; \textit{oscillate body} generates an oscillation in the whole platform by an angle $\theta$; \textit{move shoulder} moves the shoulders to a desired angle $\theta$; \textit{oscillate shoulder} oscillates the shoulders by a given angle $\theta$; \textit{move torso} moves the torso to a desired angle in $yaw$, $pitch$ and $roll$; and \textit{oscillate torso} oscillates the shoulders by a given angle $\theta$. The drivers for these actions were implemented for each platform. But, they were grouped by an interface, which hides the existence of them to the rest of the system.
